---
title: "Kiosk & App Reporting"
author: "Caiwen Li"
date: "10/15/2019"
output: html_document
---
## How to run this report? 

# Step 1: make sure your adobe token and ps are correct and Azure database user & ps are correct  
# Step 2: Run all the chunks except the last 2 chunks (Write data & Dream query table)
# Step 3: Change the saving path to your desktop path and run "write all data" chunk
# Step 3: Check your path whether have all the data saved 
# Step 4: Open the tableau flow updated the files path to yours and run the flow
# Step 5: Use tableau server log into the report and refrensh the report (make sure you have the access to this report)
# Step 6: Double check no numbers are off in the report and send to the product team (DCX)

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

```{r adobe connection}
library(RSiteCatalyst)
library(RPostgreSQL)
library(dplyr)
library(dbplyr)
library(tidyr)
library(data.table)
library(lubridate)
library(reshape2)
library(stringr)
SCAuth("caiwenli@rccl.com:RCCI", "3e7a72d82de775fb55c31f4dcc51b4e0")
```

```{r date setting}
excalibur.production <- "rcciexcaliburprod"
start.date <- as.character(Sys.Date() - wday(Sys.Date())- 83)
end.date <- as.character(Sys.Date() - wday(Sys.Date()))
```

```{r kiosk ship segments building}
# s300006910_5ac248b259161d7157e75c01 Kiosk Only
# s300006910_59cbc683e3d26c79ed095ac0 excluding appstarting
# s300006910_5aabf2d3de3c976aada2a8d8 Company Sailing Visitors
# Last segment is the ship IP list segment
Symphony <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5ab577e1c477fc1701401763")
Harmony <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5bf461955fe71e04abe23a0b")
Mariner <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5b520e794ecbca71d1f54df4")
Edge <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5beef7c04618f61c4c0ebabb")
Quantum <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5c36662f9e1245499f62e70c")
Spectrum <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5cac9e5f9e12451d042e5056")
Ovation <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5ceec3dfd4e3251e3d21e545")
Anthem <- c("s300006910_5ac248b259161d7157e75c01","s300006910_59cbc683e3d26c79ed095ac0","s300006910_5aabf2d3de3c976aada2a8d8","s300006910_5cde03e23217c900b1b74290")

kiosk.ship.segment.list <- as.list.data.frame(cbind(Symphony,Harmony,Mariner,Edge,Quantum,Spectrum,Ovation,Anthem))

```

```{r kiosk ship all metrics pull}
kiosk.ship.events.total <- NULL
for (i in 1: ncol(kiosk.ship.segment.list))
{
kiosk.ship.events <- QueueOvertime(excalibur.production,
                                        start.date,
                                        end.date,
                                        metrics  = c("event139"
                                                 ,"event182"
                                                 ,"event183"
                                                 ,"event292"
                                                 ,"event293"
                                                 ,"event294"
                                                 ,"event296"
                                                 ,"event297"
                                                 ,"event298"
                                                 ,"event299"
                                                 ,"event300"
                                                 ,"event350"
                                                 ,"event353"
                                                 ,"event354"
                                                 ,"event355"
                                                 ,"event356"
                                                 ,"event357"
                                                 ,"event359"
                                                 ,"event360"
                                                 ,"event402"
                                                 ,"event403"
                                                 ,"event406"
                                                 ,"event407"
                                                 ,"event150"
                                                 ,"event361"
                                                 ,"event138" ## Kiosk SeaPass Login (e138)
                                                 ,"event181" ## Kiosk Welcome Login Sea Pass (e181)
                                                 ,"event351" ## Kiosk Welcome Screen Tap (e351)
                                                 ,"event352" ## Kiosk Manual Login (e352)
                                                 ,"event358" ## Kiosk "Reserve Now" (e358)
                                                 ),
                                    max.attempts = 1000000,
                                    date.granularity = "day",
                                    segment.id = kiosk.ship.segment.list[,i]) 
    kiosk.ship.events.total <- rbind(kiosk.ship.events.total, kiosk.ship.events)
}

# Fix the segment name and get ship name
ship.name <- as.data.frame(unlist(lapply(strsplit(as.character(kiosk.ship.events.total$segment.name), "AND"), '[[', 4)))
colnames(ship.name) <- c("ship.name")
ship.name.fix <- as.data.frame(unlist(lapply(strsplit(as.character(ship.name$ship.name), " "), '[[', 2)))
colnames(ship.name.fix) <- c("ship.name")

# Fix date type & select the columns 
kiosk.ship.events.total <- cbind(ship.name.fix, kiosk.ship.events.total)
kiosk.ship.events.total$datetime <- as.Date(kiosk.ship.events.total$datetime)
kiosk.ship.events.total <- kiosk.ship.events.total[,c(1,2,3,5,9:38)]

colnames(kiosk.ship.events.total) <- c("Ship Code"
                                      ,"Product Booking Date"
                                      ,"Product Booking Day"
                                      ,"Product Booking Month"
                                      ,"Kiosk SeaPass Unavailable (e139)"
                                      ,"Kiosk Login Incorrect Details Error (e182)" ### Stopped using since May 2019
                                      ,"Kiosk Res Link Incorrect Details Error (e183)"
                                      ,"Edit Day (e292)"
                                      ,"Edit Guests (e293)"
                                      ,"Edit Product (e294)"
                                      ,"Select Time (e296)"
                                      ,"See Others Products(e297)"
                                      ,"Select Guests (e298)"
                                      ,"Select Day (e299)"
                                      ,"Booking Errors (e300)"
                                      ,"View Terms & Conditions (e350)"
                                      ,"Kiosk Exit (e353)"
                                      ,"Kiosk View Booked Excursions (e354)"
                                      ,"Kiosk Day Picker (e355)"
                                      ,"Kiosk Activity Overview Tap (356)"
                                      ,"Kiosk Back Arrow (e357)"
                                      ,"Kiosk Logout Continue Booking (e359)"
                                      ,"Kiosk Logout Done Booking (e360)"
                                      ,"Booking Cancel Step 1 (e402)"
                                      ,"Booking Cancel Step 2 (e403)"
                                      ,"Booking Keep Res. (e406)"
                                      ,"Booking Cannot Cancel Client Side (e407)"
                                      ,"ReservationLinkGuests (e150)"
                                      ,"Kiosk Auto Log Out (e361)"
                                      ,"Kiosk SeaPass Login (e138)"
                                      ,"Kiosk Welcome Login Sea Pass (e181)"
                                      ,"Kiosk Welcome Screen Tap (e351)"
                                      ,"Kiosk Manual Login (e352)"
                                      ,"Kiosk Reserve Now (e358)"
                                      )

kiosk.ship.events.total <- kiosk.ship.events.total %>% 
    mutate(`Total Logins` = `Kiosk SeaPass Login (e138)`+ `Kiosk Manual Login (e352)` + `Kiosk Welcome Login Sea Pass (e181)`,
           `Total Welcome Page Views` = `Kiosk Welcome Login Sea Pass (e181)`+ `Kiosk Welcome Screen Tap (e351)` + `Kiosk Manual Login (e352)` + `Kiosk SeaPass Login (e138)`)

kiosk.ship.total <- NULL
for (i in 1: ncol(kiosk.ship.segment.list))
{
  kiosk.ship.events <- QueueTrended(excalibur.production,
                                    start.date,
                                    end.date,
                                    metrics  = c("revenue"
                                                 ,"orders"
                                                 ,"units"
                                                 ,"pageviews"
                                                 ,"cm300006910_5dcae679d7e89d405a28b697" ## Product Views
                                    ),
                                    c("product"),
                                    top = 50000,
                                    date.granularity = "day",
                                    segment.id = kiosk.ship.segment.list[,i],
                                    classification = "Product Category") 
  kiosk.ship.total <- rbind(kiosk.ship.total, kiosk.ship.events)
}
kiosk.ship.total$datetime <- as.Date(kiosk.ship.total$datetime)
kiosk.ship.total <- kiosk.ship.total %>% 
  filter(!name %in% "::unspecified::") 

ship.name <- as.data.frame(unlist(lapply(strsplit(as.character(kiosk.ship.total$segment.name), "AND"), '[[', 4)))
colnames(ship.name) <- c("ship.name")

ship.name.fix <- as.data.frame(unlist(lapply(strsplit(as.character(ship.name$ship.name), " "), '[[', 2)))
colnames(ship.name.fix) <- c("ship.name")
kiosk.ship.total <- cbind(ship.name.fix, kiosk.ship.total)

kiosk.ship.total <- kiosk.ship.total[,c(1,2,3,5:9)]

colnames(kiosk.ship.total) <- c("Ship Code"
                                ,"Product Booking Date"
                                ,"Product Cate"
                                ,"Revenue"
                                ,"Orders"
                                ,"Units"
                                ,"Page Views"
                                ,"Product Views"
                                )   

kiosk.ship.total$key <- paste0(kiosk.ship.total$`Product Booking Date`, kiosk.ship.total$`Ship Code`, sep = "")
kiosk.ship.events.total$key <- paste0(kiosk.ship.events.total$`Product Booking Date`, kiosk.ship.events.total$`Ship Code`, sep = "")

kiosk.ship.events.all <- kiosk.ship.total %>% 
  inner_join(kiosk.ship.events.total, by = "key")

kiosk.ship.events.all$key <- NULL
kiosk.ship.events.all$`Ship Code.x` <- NULL
kiosk.ship.events.all$`Product Booking Date.x` <- NULL

## Check on this next week
kiosk.ship.events.all <- kiosk.ship.events.all[,c(8:10,7,1,2:6,11:42)] %>% 
  mutate(`Product Booking Day` = weekdays(`Product Booking Date.y`),
         `Product Booking Wk` = floor_date(as.Date(`Product Booking Date.y`, "%m/%d/%Y"), unit="week"))

colnames(kiosk.ship.events.all)[1] <- "Product Booking Date"
colnames(kiosk.ship.events.all)[4] <- "Ship Code"
rm(kiosk.ship.total)
```

```{r kiosk fallout data pull}
falloutpattern <- c("kiosk:welcome", "kioskshorex:listview", "kioskshorex:reservationwhosgoing", "kioskshorex:reservationproductbyvenue", "kioskshorex:reservationstatement")

kiosk.fallout.total <- NULL
for (i in 1: ncol(kiosk.ship.segment.list))
{
  kiosk.fallout <- QueueFallout(excalibur.production,
                                start.date,
                                end.date,
                                metric = "pageviews",
                                element = "page",
                                falloutpattern,
                                segment.id = kiosk.ship.segment.list[,i])
  kiosk.fallout.total <- rbind(kiosk.fallout.total, kiosk.fallout)
}

ship.name <- as.data.frame(unlist(lapply(strsplit(as.character(kiosk.fallout.total$segment.name), "AND"), '[[', 4)))
colnames(ship.name) <- c("ship.name")

ship.name.fix <- as.data.frame(unlist(lapply(strsplit(as.character(ship.name$ship.name), " "), '[[', 2)))
colnames(ship.name.fix) <- c("ship.name")
kiosk.fallout.total <- cbind(ship.name.fix, kiosk.fallout.total)
kiosk.fallout.total <- kiosk.fallout.total[,c(1,2,4)]

kiosk.fallout.total$name <- gsub("kiosk:welcome", "Welcome Screen", kiosk.fallout.total$name)
kiosk.fallout.total$name <- gsub("kioskshorex:listview", "Browse List", kiosk.fallout.total$name)
kiosk.fallout.total$name <- gsub("kioskshorex:reservationwhosgoing", "Who's Going", kiosk.fallout.total$name)
kiosk.fallout.total$name <- gsub("kioskshorex:reservationproductbyvenue", "Product by Venue", kiosk.fallout.total$name)
kiosk.fallout.total$name <- gsub("kioskshorex:reservationstatement", "Checkout Page", kiosk.fallout.total$name)

kiosk.fallout.total$pageviews <- as.character(kiosk.fallout.total$pageviews)
```

```{r app ship segments building}
# s300006910_59c41d59c06c5c10c89f449d App Only
# s300006910_59de69e94cfe090d7d6edecf Onship Only
# Last segment is the ship IP list segment
Adventure <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5b929acef73f23559bfd263b")
Allure <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5bd20966be6bf235d072f0f2")
Anthem <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5cde03e23217c900b1b74290")
Brilliance <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5bae3a13e50ca00d616e1e26")
Constellation <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5a37eb6d1d43f6274e1980b6")
Edge <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5beef7c04618f61c4c0ebabb")
Empress <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5cddfa99d48757449048e91d")
Enchantment <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5a65f57601e823672540f285")
Equinox <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5ba108de11a9b40d60e3c3d7")
Grandeur <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5cde014cb8dcd954229f1316")
Harmony <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5bf461955fe71e04abe23a0b")
Independence <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5b929c7222fa995faeee4a9e")
Liberty <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5bf463bc0725624af0b617bc")
Majesty <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5bbcf4a4cfb2522b57b3d224")
Mariner <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5b520e794ecbca71d1f54df4")
Millennium <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5c3661517d03f6237a695ea9")
Navigator <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5c59a25dc8976708f490ad3e")
Oasis <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_59e4a689a5bb5773019e3f76")
Ovation <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5ceec3dfd4e3251e3d21e545")
Pursuit <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5c11383bb81a6c1660a4faff")
Quantum <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5c36662f9e1245499f62e70c")
Reflection <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5ab577805ef3a55946dce425")
Rhapsody <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5cde04d4e445484643f500b0")
Serenade <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5a3c3869535e3b166819b18f")
Spectrum <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5cac9e5f9e12451d042e5056")
Summit <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5c59a3f90d9f0c71f0777def")
Symphony <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5ab577e1c477fc1701401763")
Vision <- c("s300006910_59c41d59c06c5c10c89f449d", "s300006910_59de69e94cfe090d7d6edecf","s300006910_5c365c990d9f0c71f0ac9604")

app.ship.segment.list <- as.list.data.frame(cbind(Adventure,Allure,Brilliance,Constellation,Edge,Enchantment,Equinox,Harmony,Independence,Majesty,Mariner,Millennium,Navigator,Oasis,Pursuit,Quantum,Reflection,Serenade,Spectrum,Summit,Symphony,Vision))

```

```{r app ship & product all metrics pull}
app.ship.product.total <- NULL
for (i in 1: ncol(app.ship.segment.list))
{
  app.ship.product <- QueueTrended(excalibur.production,
                                   start.date,
                                   end.date,
                                   metrics  = c("revenue"
                                                ,"orders"
                                                ,"units"
                                                ,"pageviews"
                                                ,"uniquevisitors"
                                                ,"visits"
                                                ,"cm300006910_5dcae679d7e89d405a28b697" ## Product Views
                                                ,"cm300006910_5dcad4e9cffa482fc832abc8" ## DCX Pages - Unique Visitor
                                                ,"cm300006910_5dcad50c4252e93b18270dd3" ## DCX Pages - Visits
                                                ,"cm300006910_5dcad63412ea55187d74c45f" ## Bookable - Product Views
                                                ,"cm300006910_5dcad819b193a53c9b616c1f" ## Reserve Now Tap
                                                ),
                                   c("product"),
                                   top = 50000,
                                   max.attempts = 1000000,
                                   date.granularity = "week",
                                   segment.id = app.ship.segment.list[,i],
                                   classification = "Product Category") 
  app.ship.product.total <- rbind(app.ship.product.total, app.ship.product)
}

ship.name <- as.data.frame(unlist(lapply(strsplit(as.character(app.ship.product.total$segment.name), "AND"), '[[', 3)))
colnames(ship.name) <- c("ship.name")
ship.name.fix <- as.data.frame(unlist(lapply(strsplit(as.character(ship.name$ship.name), " "), '[[', 2)))
colnames(ship.name.fix) <- c("ship.name")
app.ship.product.total <- cbind(ship.name.fix, app.ship.product.total)
app.ship.product.total$datetime <- as.Date(app.ship.product.total$datetime)

app.ship.product.total <- app.ship.product.total[,c(1:3, 5:15)]

colnames(app.ship.product.total) <- c("Ship Code"
                                      ,"Product Booking Date"
                                      ,"Product Cate"
                                      ,"Revenue"
                                      ,"Orders"
                                      ,"Units"
                                      ,"Page Views"
                                      ,"Unique Visitor"
                                      ,"Visits"
                                      ,"Product Views"
                                      ,"DCX - Unique Visitor"
                                      ,"DCX - Visits"
                                      ,"Bookable - Product Views"
                                      ,"Reserve Now Tap")

app.ship.product.total <- app.ship.product.total %>% 
  filter(!`Product Cate` %in% "::unspecified::",
         !`DCX - Visits` %in% 0) 

app.ship.events.total <- NULL
for (i in 1: ncol(app.ship.segment.list))
{
  app.ship.events <- QueueOvertime(excalibur.production,
                                     start.date,
                                     end.date,
                                     metrics  = c("event150"
                                                  ,"event292"
                                                  ,"event293"
                                                  ,"event294"
                                                  ,"event296"
                                                  ,"event297"
                                                  ,"event298"
                                                  ,"event299"
                                                  ,"event300"
                                                  ,"event310"
                                                  ,"event311"
                                                  ,"event350"
                                                  ,"event372"
                                                  ,"event402"
                                                  ,"event414"
                                                  ,"event415"
                                                  ,"event416"
                                                  ,"event417"
                                                  ,"event487"
                                                  ,"event488"
                                                  ,"revenue"
                                                  ,"orders"
                                                  ,"units"
                                                  ,"pageviews"
                                                  ,"uniquevisitors"
                                                  ,"visits"
                                                  ,"totaltimespent"),
                                     max.attempts = 1000000,
                                     date.granularity = "day",
                                     segment.id = app.ship.segment.list[,i]) 
  app.ship.events.total <- rbind(app.ship.events.total, app.ship.events)
}

ship.name <- as.data.frame(unlist(lapply(strsplit(as.character(app.ship.events.total$segment.name), "AND"), '[[', 3)))
colnames(ship.name) <- c("ship.name")
ship.name.fix <- as.data.frame(unlist(lapply(strsplit(as.character(ship.name$ship.name), " "), '[[', 2)))
colnames(ship.name.fix) <- c("ship.name")
app.ship.events.total <- cbind(ship.name.fix, app.ship.events.total)
app.ship.events.total$datetime <- as.Date(app.ship.events.total$datetime)
app.ship.events.total <- app.ship.events.total[,c(1,2,3,5,9:35)]

colnames(app.ship.events.total) <- c("Ship Code"
                                     ,"Product Booking Date"
                                     ,"Product Booking Day"
                                     ,"Product Booking Month"
                                     ,"ReservationLinkGuests (e150)"
                                     ,"Edit Day (e292)"
                                     ,"Edit Guests (e293)"
                                     ,"Edit Product (e294)"
                                     ,"Select Time (e296)"
                                     ,"See Others Products(e297)"
                                     ,"Select Guests (e298)"
                                     ,"Select Day (e299)"
                                     ,"Booking Errors (e300)"
                                     ,"SubCategory/Filter Tap (e310)"
                                     ,"Activity Overview Tap (e311)"
                                     ,"View Terms & Conditions (e350)"
                                     ,"Reserve Now (e372)"
                                     ,"Booking Cancel Step 1 (e402)"
                                     ,"Reservation Cancel Start (414)"
                                     ,"Res Activity Tap (e415)"
                                     ,"Booking Remove Guest Start (416)"
                                     ,"removeGuestsConfirm (417)"
                                     ,"Reservation Seating Preference (e487)"
                                     ,"Add Payment Method (e488)"
                                     ,"Revenue"
                                     ,"Orders"
                                     ,"Units"
                                     ,"Page Views"
                                     ,"Unique Visitor"
                                     ,"Visits"
                                     ,"Total Time Spent")
```

```{r app fallout data pull- booking funnel flow}
app.funnel.total <- NULL
for (i in 1: ncol(app.ship.segment.list))
{
  app.funnel <- QueueRanked(excalibur.production,
                              start.date,
                              end.date,
                              metric = "pageviews",
                              element = "page",
                              search	 = c("reservationwhosgoing", "reservationselectday", "reservationproductbyvenue", "reservationstatement"),
                              segment.id = app.ship.segment.list[,i])
  app.funnel.total <- rbind(app.funnel.total, app.funnel)
}

ship.name <- as.data.frame(unlist(lapply(strsplit(as.character(app.funnel.total$segment.name), "AND"), '[[', 3)))
colnames(ship.name) <- c("ship.name")

ship.name.fix <- as.data.frame(unlist(lapply(strsplit(as.character(ship.name$ship.name), " "), '[[', 2)))
colnames(ship.name.fix) <- c("ship.name")
app.funnel.total <- cbind(ship.name.fix, app.funnel.total)
app.funnel.total <- app.funnel.total[,c(1,2,4)]

app.funnel.total <- app.funnel.total %>% 
  separate(name, c("Product Cate", "Screen Name", sep = ":"))

app.funnel.total <- app.funnel.total[,c(1:3,5)]
app.funnel.total$pageviews <- as.character(app.funnel.total$pageviews)

app.funnel.total$`Screen Name` <- gsub("reservationselectday", "Select Day", app.funnel.total$`Screen Name`)
app.funnel.total$`Screen Name` <- gsub("reservationstatement", "Checkout Page", app.funnel.total$`Screen Name`)
app.funnel.total$`Screen Name` <- gsub("reservationwhosgoing", "Who's Going", app.funnel.total$`Screen Name`)
app.funnel.total$`Screen Name` <- gsub("reservationproductbyvenue", "Product by Venue", app.funnel.total$`Screen Name`)
```

```{r merge adobe data for overall numbers}
kiosk.append <- kiosk.ship.events.all %>% 
  mutate(Channel = "Kiosk")
tbl_vars(kiosk.append)

kiosk.append <- kiosk.append[,c(44,43,4:10,40)] %>% 
  group_by(Channel, `Product Booking Wk`, `Ship Code`, `Product Cate`) %>% 
  summarise(Revenue = sum(Revenue),
            Orders = sum(Orders),
            Units = sum(Units),
            `Page Views` = sum(`Page Views`),
            `Product Views` = sum(`Page Views`),
            `Reserve Now` = sum(`Kiosk Reserve Now (e358)`))

colnames(kiosk.append) <- c("Channel", "Product Booking Wk", "Ship Code", "Product Cate", "Revenue", "Orders", "Units", "Page Views", "Product Views", "Reserve Now")
app.append <- app.ship.product.total %>% 
  mutate(Channel = "App")

app.append <- app.append[,c(15,2,1,3:7,10,14)]
colnames(app.append) <- c("Channel", "Product Booking Wk", "Ship Code", "Product Cate", "Revenue", "Orders", "Units", "Page Views", "Product Views", "Reserve Now")
kiosk.append$`Product Booking Wk` <- as.Date(kiosk.append$`Product Booking Wk`)
app.kiosk.overall <- dplyr::bind_rows(kiosk.append, app.append)

```

```{r azure data - transactions for app & kiosk}
library(odbc)
con.microsoft.sql <- DBI::dbConnect(odbc::odbc(),
                                    Driver   = "SQL Server",
                                    Server   = "rcclanalyticssql.database.windows.net",
                                    Database = "rcclanalytics",
                                    UID      = "caiwenli",
                                    PWD      = "xxx",
                                    Port     = 1433)

dbo.mia <- paste("SELECT T.BRAND,
       T.SHIP_CODE,
       T.SAIL_DATE,
       T.VOYAGE_RETURN_DATE,
       CONCAT(T.SHIP_CODE,CONVERT(VARCHAR(10), T.SAIL_DATE, 120)) THE_KEY_T,
       T.RDSS_PRODUCT_CODE,
       T.ASR_BOOKING_ID,
       T.ORDER_ID,
       T.CRUISE_BOOKING_ID,
       T.BUYER_ID,
       T.TOTAL_PAYMENT_AMT,
       T.PRODUCT_ID_CHAR,
       T.PRODUCT_NAME,
       T.PRODUCT_BOOKING_DTM,
       T.CHANNEL,
       T.REVENUE_PROD,
       T.BOOKING_STATUS_DESC,  
       T.OWNER_DESC,
       V.SHIP_CODE,
       V.SHIP_DEPARTURE_DATE,
       CONCAT(V.SHIP_CODE,V.SHIP_DEPARTURE_DATE) THE_KEY_V,
       V.PRODUCT_CODE,
       V.VOYAGE_ORIGINATING_PORT_DESC,
       V.ITINERARY_DESC,
       V.ITINERARY_DAYS_QTY
FROM RCCLAnalytics.dbo.MIA_MobileBookingsRevMod T
LEFT JOIN RCCLAnalytics.dbo.VDC_VOYAGE V
ON CONCAT(V.SHIP_CODE,V.SHIP_DEPARTURE_DATE) = CONCAT(T.SHIP_CODE,CONVERT(VARCHAR(10), T.SAIL_DATE, 120)) 
WHERE T.PRODUCT_BOOKING_DTM BETWEEN GETDATE() - DATEPART(WEEKDAY, GETDATE())- 83 AND GETDATE() - DATEPART(WEEKDAY, GETDATE())
      AND T.CHANNEL IN ('Excalibur App', 'Excalibur Kiosk')", sep="")

dbo.mia.query <- dbGetQuery(con.microsoft.sql, dbo.mia)

## dbo.mia.query <- tidyr::separate(dbo.mia.query, RDSS_PRODUCT_CODE, into = c("name", "value"), "(?<=[A-Z])(?=[0-9])") %>% 
##   select(1:4, 6:17)

## colnames(dbo.mia.query)[4] <- "DESTINATION_CODE"
tbl_vars(dbo.mia.query)
dbo.mia.query <- dbo.mia.query[,c(1:4, 6:18, 22:25)]
dbo.mia.query <- dbo.mia.query %>% 
  mutate(DAY_ONSHIP = as.Date(as.character(PRODUCT_BOOKING_DTM)) - as.Date(as.character(SAIL_DATE)) + 1,
         VOYAGE_ID = paste0(dbo.mia.query$SHIP_CODE, sep = "_", dbo.mia.query$SAIL_DATE) )

dbo.mia.query$DAY_ONSHIP <- as.numeric(dbo.mia.query$DAY_ONSHIP)

```

```{r YTD YOY Comparing}
dbo.mia.ly.ytd <- paste("SELECT T.BRAND,
       T.SHIP_CODE,
       T.SAIL_DATE,
       SUM(T.TOTAL_PAYMENT_AMT) TOTAL_REV,
       T.CHANNEL,
       DATEPART(wk,T.PRODUCT_BOOKING_DTM) WEEK_NUM,
       DATEPART(year,T.PRODUCT_BOOKING_DTM) YEAR_NUM,
       T.REVENUE_PROD,
       T.BOOKING_STATUS_DESC,
       T.OWNER_DESC
FROM RCCLAnalytics.dbo.MIA_MobileBookingsRevMod T
WHERE T.PRODUCT_BOOKING_DTM BETWEEN '2019-01-01' AND GETDATE() - DATEPART(WEEKDAY, GETDATE()) - 365
      AND T.CHANNEL IN ('Excalibur App', 'Excalibur Kiosk')
GROUP BY DATEPART(year,T.PRODUCT_BOOKING_DTM),
         DATEPART(wk,T.PRODUCT_BOOKING_DTM),
         T.CHANNEL,
         T.BRAND,
         T.SHIP_CODE,
         T.SAIL_DATE,
         T.REVENUE_PROD,
         T.BOOKING_STATUS_DESC,
         CONCAT(T.SHIP_CODE, T.SAIL_DATE),
         T.OWNER_DESC", sep="")

dbo.mia.ty.ytd <- paste("SELECT T.BRAND,
       T.SHIP_CODE,
       T.SAIL_DATE,
       SUM(T.TOTAL_PAYMENT_AMT) TOTAL_REV,
       T.CHANNEL,
       DATEPART(wk,T.PRODUCT_BOOKING_DTM) WEEK_NUM,
       DATEPART(year,T.PRODUCT_BOOKING_DTM) YEAR_NUM,
       T.REVENUE_PROD,
       T.BOOKING_STATUS_DESC,
       T.OWNER_DESC
FROM RCCLAnalytics.dbo.MIA_MobileBookingsRevMod T
WHERE T.PRODUCT_BOOKING_DTM BETWEEN '2020-01-01' AND GETDATE() - DATEPART(WEEKDAY, GETDATE())
      AND T.CHANNEL IN ('Excalibur App', 'Excalibur Kiosk')
GROUP BY DATEPART(year,T.PRODUCT_BOOKING_DTM),
         DATEPART(wk,T.PRODUCT_BOOKING_DTM),
         T.CHANNEL,
         T.BRAND,
         T.SHIP_CODE,
         T.SAIL_DATE,
         T.REVENUE_PROD,
         T.BOOKING_STATUS_DESC,
         CONCAT(T.SHIP_CODE, T.SAIL_DATE),
         T.OWNER_DESC", sep="")

dbo.mia.ly.ytd.query <- dbGetQuery(con.microsoft.sql, dbo.mia.ly.ytd)
dbo.mia.ty.ytd.query <- dbGetQuery(con.microsoft.sql, dbo.mia.ty.ytd)

dbo.mia.ytd.query <- rbind(dbo.mia.ty.ytd.query, dbo.mia.ly.ytd.query)
dbo.mia.ytd.query <- dbo.mia.ytd.query %>% 
  mutate(VOYAGE_ID = paste0(dbo.mia.ytd.query$SHIP_CODE, sep = "_", dbo.mia.ytd.query$SAIL_DATE) )

```

```{r write all the data --- CHANGE THE PATH}
write.csv(kiosk.ship.events.all,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/kiosk.ship.events.all.csv")
write.csv(kiosk.fallout.total,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/kiosk.fallout.total.csv")

write.csv(dbo.mia.query,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/dbo.mia.query.csv")
write.csv(dbo.mia.ytd.query,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/dbo.mia.ytd.query.csv")

write.csv(app.ship.product.total,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/app.ship.product.total.csv")
write.csv(app.ship.events.total,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/app.ship.events.total.csv")
write.csv(app.funnel.total,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/app.funnel.total.csv")

write.csv(app.kiosk.overall,"C:/Users/7005773/Desktop/Work/App & Kiosk Weekly Report/Processed Data/app.kiosk.overall.csv")
```

```{r dream query - azure data - transactions for app & kiosk --- DONT RUN}
options(java.parameters = "-Xmx8g")
library("RJDBC")
library(RJDBC)
drv <- JDBC("oracle.jdbc.OracleDriver",classPath="C:/users/7005773/Downloads/ojdbc6.jar")
con.oracle <- dbConnect(drv, "jdbc:oracle:thin:@//dmmktgp_exa.rccl.com:1689/DMMKTGP.RCCL.COM", "xx","xx")

pcp.transactional.level <- paste("SELECT T.SHIP_CODE,
       T.SAIL_DATE,
       TO_CHAR(T.PASSENGER_ID) PASSENGER_ID,
       TO_CHAR(T.BOOKING_ID) AS CRUISE_BOOKING_ID,
       CONCAT(CONCAT(CONCAT(T.BOOKING_ID, T.PASSENGER_ID), T.SAIL_DATE), T.SHIP_CODE) AS THE_KEY,
       T.PRODUCT_ID,
       T.ASR_BOOKING_ID,
       T.ORDER_ID,
       T.ADJUSTED_OWNER_DESC,
       T.COMPONENT_NAME,
       T.ASR_PRODUCT_BOOKING_DTM,
       T.CHANNEL,
       T.OWNER_DESC,
       T.BOOKING_STATUS_NAME,
       T.TOTAL_REVENUE_USD,
       T.TOUR_DURATION_HR,
       T.AMT_GUEST_PAID_BKC,
       T1.BOOKING_ID,
       T1.BRAND,
       T1.RDSS_PRODUCT_CODE,
       T1.META_PRODUCT_CODE,
       T1.BOOKING_TYPE,
       T1.NET_TICKET_REVENUE_USD,
       T1.PASSENGER_ID,
       CONCAT(CONCAT(CONCAT(T1.BOOKING_ID, T1.PASSENGER_ID), T1.SAIL_DATE), T1.SHIP_CODE) AS THE_KEY,
       T1.SAIL_DATE,
       T1.SAIL_NIGHTS,
       T1.BOOKING_STATUS,
       T1.PAX_AGE,
       T1.PAX_CITIZENSHIP,
       T1.PAX_DOCUMENTATION_LANGUAGE,
       T1.PAX_GENDER_CODE,
       T1.RATE_CAT_CLASS,
       CASE WHEN T1.PAX_LOYALTY_NUMBER IS NOT NULL THEN 1 ELSE 0 END AS LOYALTY_STATUS
FROM DIGITALBI.DREAM_PCP_ASR_DETAIL T
LEFT JOIN DIGITALBI.DREAM_CRUISE_OBJECT T1
ON CONCAT(CONCAT(CONCAT(T1.BOOKING_ID, T1.PASSENGER_ID), T1.SAIL_DATE), T1.SHIP_CODE) = CONCAT(CONCAT(CONCAT(T.BOOKING_ID, T.PASSENGER_ID), T.SAIL_DATE), T.SHIP_CODE) 
WHERE T.CHANNEL IN ('Mobile App', 'Kiosk')
      AND T.ASR_PRODUCT_BOOKING_DTM BETWEEN '2019-01-01' AND TRUNC(SYSDATE) - (TO_CHAR(SYSDATE, 'd')-1)", sep="")

pcp.transactional.level.query <- dbGetQuery(con.oracle, pcp.transactional.level)

```
